Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-25 paper/presentation/DASFAA_presentation.tex
finish the example, [todo] overview of our solution

@@

%------------------------------
%page 6
\begin{frame}
Much easier to detect the event on the time series of word "hood" related to \textit{Military}.
\frametitle{An Example}	
\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=1.0\columnwidth]{../img/hood.pdf}
        \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}. Refer the event to \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
        \label{fig:hood}
\end{figure}

@@

%------------------------------
%page 7
\begin{frame}
\frametitle{The insights on the example}

@@

%------------------------------
%page 8
\begin{frame}
\frametitle{Overview of our method}

@@

%------------------------------
%page 9
\begin{frame}
\frametitle{\textsc{TransDetector}: Phrase 1}	
\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=0.5\columnwidth]{../img/initializationExample.pdf}
        \caption{Extracting Category-Level Topics in Knowledge Base via its three fold hierarchical structure, taking \textit{Military} as an example.}
        \label{fig:hood}
\end{figure}

@@

%\end{comment}

>>>>

%used for colored block
\usepackage[listings,theorems]{tcolorbox}

@@

%------------------------------
%page 6
\begin{frame}
\textbf{Much easier} to detect the event on the time series of word ``hood" related to \textit{Military}, \textbf{without adjusting the threshold}.
\frametitle{An Example}	
\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=1.0\columnwidth]{../img/hood.pdf}
        \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}. Refer the event to \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
        \label{fig:hood}
\end{figure}

@@

%------------------------------
%page 7
\begin{frame}
\frametitle{The insights on the example}	
\begin{columns}[onlytextwidth, t]
\column{0.48\linewidth}
    \begin{tcolorbox}[colback=red!5,colframe=red!5]
    Knowledge Base
        \begin{itemize}
            \item Well organized
            \item Constructed elaborately
            \item full of rich information
        \end{itemize}
    \end{tcolorbox}

\column{0.48\linewidth}
    \begin{tcolorbox}[colback=red!5,colframe=red!5]
    Microblog stream
        \begin{itemize}
            \item Short length
            \item Fast changing
            \item High noise
        \end{itemize}
    \end{tcolorbox}
\end{columns}

\begin{tcolorbox}[colback=red!5,colframe=red!75!black]
The benefit of \textbf{enriching the semantics} and \textbf{filtering out noise} by Knowledge Base for microblogs is attractive.
\\~\\
But it's expensive to retrieve every word of tweets in the Knowledge Base.
\end{tcolorbox}

@@

%------------------------------
%page 8
\begin{frame}
\frametitle{Overview of our solution}

@@

\begin{comment}
%------------------------------
%page 9
\begin{frame}
\frametitle{\textsc{TransDetector}: Phrase 1}	
\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=0.5\columnwidth]{../img/initializationExample.pdf}
        \caption{Extracting Category-Level Topics in Knowledge Base via its three fold hierarchical structure, taking \textit{Military} as an example.}
        \label{fig:hood}
\end{figure}

@@

\end{comment}
